Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-23 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \NewDocumentCommand{\newInterval}{o o o}{...} Added...
revised_prop_letter_ajhs.tex preamble updated...
prop.bib @Misc{HKSS1999} @Unpublished{HKSS1999apsrev4} Added...
revised_prop_letter_ajhs.tex \section{Experimental Data and \texorpdfstring{$\delta$}{delta}-determinism} Fix typos...

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\text{\wesa{impossible}}}}
\newcommand{\likely}{{\text{\wesa{likely}}}}
\newcommand{\unlikely}{{\text{\wesa{unlikely}}}}
\newcommand{\necess}{{\text{\wesa{certain}}}}
\newcommand{\unknown}{{\text{\wesa{unknown}}}}
\newcommand{\midd}{{\text{\wesa{middle}}}}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{L{#1}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{R{#1}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{d}
\newcommand{\rmi}{i}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\eventsC}{\ensuremath{\events_{C}}}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}

@@

\begin{table*}
\caption{\label{tab:probability-measures}Possible probability measures on
a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
by $P$.}
\centering{}%
\begin{tabular}{cccccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\end{table*}
It is Meyer's great insight to realize that the Kochen-Specker theorem can be nullified 
by replacing the field of the reals by rational numbers.  In other
words, Meyer exclusively attributes finite-precision errors to the
description of the states defined in a general Hilbert space. The
response of Mermin, argues against Meyer's interpretation but accepts
his framework. More generally, there have been responses that argue
that the effect of finite-precision measurements on the Kochen-Specker
theorem requires a different approach altogether (see for example Ax
and Kochen's communication cited by Cabello~\cite{Cabello2002}). Our
approach is agnostic about attributing elements of reality to the
state function (as Meyer did). We simply attribute lack of certainty
to the uncertain results obtained through the use of a measuring
instrument. Thus, the parameter~$\delta$ in our framework reflects
insufficient knowledge of the experimenter, which could be due to a
variety of reasons related to imperfections of devices. For example, a
typical question that an experimenter may not be able to answer
accurately would be ``did an electron land in the left half or the
right half of the screen?''  There are cases in which the electron
would land too close to the middle of the screen for the experimenter
to be able to determine with certainty that it was left or right of
the center. We simply record this imprecision in the probability we
assign to events, and use the axioms of probability theory to argue
that a sharp transition occurs when the imprecision reaches a certain
value.

@@

To see this idea in the context of a quantum experiment, consider
a three-dimensional Hilbert space with
one-dimensional projectors~$P_{\rho}$, two-dimensional projectors
$P_{\rho}+P_{\sigma}$, and an experiment that is experiment repeated $12$
times. By the Kochen-Specker theorem, it is impossible to build a probability
measure that maps every projection to either $0=\frac{0}{12}$ or
$1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
defined in Table~\ref{tab:probability-measures} is not a QIVPM.

@@

\input{revised_prop_letter_ajhs.bbl}
% \bibliography{prop}
\end{document}

>>>>

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}

\NewDocumentCommand{\newInterval}{o o o o}{
 % \newcommand{#1}{\text{\wesa{{#2}}}}
 \newcommand{#1}{\ensuremath{\left[{#3}\right]}}
 % \newcommand{#1}{\ensuremath{I\left({#4}\right)}}
}
\newInterval[\imposs][impossible][0,0][0]
\newInterval[\likely][likely][\tfrac{1}{2},1][\tfrac{1}{2},1]
\newInterval[\unlikely][unlikely][0,\tfrac{1}{2}][0,\tfrac{1}{2}]
\newInterval[\necess][certain][1,1][1]
\newInterval[\unknown][unknown][0,1][0,1]
\newInterval[\midd][middle][\tfrac{1}{4},\tfrac{3}{4}][\tfrac{1}{4},\tfrac{3}{4}]

\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{L{#1}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{R{#1}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{d}
\newcommand{\rmi}{i}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{L{#1}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{R{#1}}}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\eventsC}{\ensuremath{\events_{C}}}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\amr}[1]{\says{green}{Amr}{#1}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\gerardo}[1]{\says{OliveGreen}{Gerardo}{#1}}
\newcommand{\andy}[1]{\says{blue}{Andy}{#1}}
% \excludecomment{suggest}
\NewDocumentEnvironment{suggest}{m m O{}}{#1{TEXT \##2 would go here. #3}}{#1{TEXT \##2 end here.}}
\NewDocumentEnvironment{oldText}{m}{\clearpage{}#1{The following is old text.}}{#1{The old text ends here.}}
\NewDocumentEnvironment{newText}{m}{\columnbreak{}#1{The following is new text.}}{#1{The new text ends here.}}

@@

\begin{table*}
\caption{\label{tab:probability-measures}Possible probability measures on
a Hilbert space of dimension~$d=3$, where $\bar{\mu}_{2}'$ and
$\bar{\mu}_{3}$ are QIVPMs while $\bar{\mu}_{0}$, $\bar{\mu}_{1}$,
and $\bar{\mu}_{2}$ are not. Events are listed in the column labeled
by $P$.}
\centering{}%
\begin{tabular}{cccccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{0}\left(P\right)$ & $\bar{\mu}_{1}\left(P\right)$ & $\bar{\mu}_{2}\left(P\right)$ & $\bar{\mu}_{2}'\left(P\right)$ & $\bar{\mu}_{3}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[0,0\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left[0,\tfrac{1}{3}\right]$ & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$ & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[1,1\right]$ & $\left[\tfrac{3}{4},1\right]$ & $\left[\tfrac{2}{3},1\right]$ & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$ & $\left[\tfrac{1}{2},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$ & $\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\end{table*}
It is Meyer's great insight to realize that the Kochen-Specker theorem
can be nullified by replacing the field of the reals by rational numbers.
In other words, Meyer exclusively attributes finite-precision errors
to the description of the states defined in a general Hilbert space.
The response of Mermin argues against Meyer's interpretation but accepts
his framework. More generally, there have been responses that argue
that the effect of finite-precision measurements on the Kochen-Specker
theorem requires a different approach altogether (see for example
Ax and Kochen's communication cited by Cabello~\cite{Cabello2002}).
Our approach is agnostic about attributing elements of reality to
the state function (as Meyer did). We simply attribute lack of certainty
to the uncertain results obtained through the use of a measuring instrument.
Thus, the parameter~$\delta$ in our framework reflects insufficient
knowledge of the experimenter, which could be due to a variety of
reasons related to imperfections of devices. For example, a typical
question that an experimenter may not be able to answer accurately
would be ``did an electron land in the left half or the right half
of the screen?'' There are cases in which the electron would land
too close to the middle of the screen for the experimenter to be able
to determine with certainty that it was left or right of the center.
We simply record this imprecision in the probability we assign to
events, and use the axioms of probability theory to argue that a sharp
transition occurs when the imprecision reaches a certain value.

@@

To see this idea in the context of a quantum experiment, consider
a three-dimensional Hilbert space with one-dimensional projectors~$P_{\rho}$,
two-dimensional projectors $P_{\rho}+P_{\sigma}$, and an experiment
that repeated $12$ times. By the Kochen-Specker theorem, it is impossible
to build a probability measure that maps every projection to either
$0=\frac{0}{12}$ or $1=\frac{12}{12}$. That is, the assignment~$\bar{\mu}_{0}$
defined in Table~\ref{tab:probability-measures} is not a QIVPM.

@@

% \input{revised_prop_letter_ajhs.bbl}
\bibliography{prop}
\end{document}
